### 2014-11-09 tex/intro.tex
starting to reorg the front matter

With the advent of object-oriented
languages that manipulate dynamically allocated data,
 .g., Java and C$++$, recent work has generalized the core ideas of 
symbolic execution to enable analysis of programs containing
complex data structures with unbounded domains, i.e., data stored
on the heap~\cite{Kiasan06,Kiasan07,GSE03}.
These techniques onstruct the heap in a lazy manner, 
deferring materialization of objects on the concrete heap until
they are needed for the analysis to proceed.
%, i.e., until execution of a statement with a  dereference expression 
%($x = r.f$).
Treatment of
heap allocated data then follows concrete program semantics 
once a heap location is materialized, resulting in a large number
of feasible concrete heap configurations, and as a result, a large
number of points of 
non-determinism to be analyzed, further exacerbating 
the state space explosion problem.

THIS PARA IS NOT QUITE RIGHT BUT THE IDEA IS STARTING TO COME OUT.
Although lazy symbolic execution techniques have been instrumental 
in enabling analysis of heap manipulating programs, they miss an
important opportunity to control the state space explosion problem
by treating only inputs with primitive types symbolically and
materializing a concrete heap. As we show in this work, the use of
a fully \emph{symbolic heap} during lazy symbolic execution, 
can improve the scalability of the analysis while maintaining
precision and efficiency. Moreover, the number of path conditions
computed by lazy symbolic execution when a symbolic heap
is used
produces considerably fewer path conditions -- a valuable benefit
for client analyses that use the results of symbolic execution,
e.g., regression analyses.

The key advantages of our approach to lazy symbolic execution
using a fully symbolic heap include:
\begin{itemize}
\item{\emph{Scalability.} Our approach constructs the symbolic
heap on-the-fly during symbolic execution and avoids creating
the additional points of non-determinism
introduced by existing lazy initialization techniques. Moreover, it explores
each execution path only once for any given set of isomorphic heaps.}
\item{\emph{Precision.} At any given point during symbolic execution, 
the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis}
\item{\emph{Expressiveness.} The symbolic heap can represent recursive 
data structures  and heap structures resulting from loops and recursive control 
structures in the analyzed code. }
 \end{itemize}

>>>>

With the advent of object-oriented languages that manipulate
dynamically allocated data, .g., Java and C$++$, recent work has
generalized the core ideas of symbolic execution to enable analysis of
programs containing complex data structures with unbounded domains,
i.e., data stored on the heap~\cite{Kiasan06,Kiasan07,GSE03}.  These
techniques construct the heap in a lazy manner, deferring
materialization of objects on the concrete heap until they are needed
for the analysis to proceed. The materilization accounts for various
heap configurations and creates non-deterministic choices for the
symbolic object to be initialized as (a) null, (b) instance of a new
reference of a compatible class, and (c) alias an previously
initialized symbolic reference. Treatment of heap allocated data then
follows concrete program semantics once a heap location is
materialized, resulting in a large number of feasible concrete heap
configurations, and as a result, a large number of points of
non-determinism to be analyzed, further exacerbating the state space
explosion problem.

\nsr{need a paragraph on heap summarization techniques}

\begin{comment}
THIS PARA IS NOT QUITE RIGHT BUT THE IDEA IS STARTING TO COME OUT.
Although lazy symbolic execution techniques have been instrumental 
in enabling analysis of heap manipulating programs, they miss an
important opportunity to control the state space explosion problem
by treating only inputs with primitive types symbolically and
materializing a concrete heap. As we show in this work, the use of
a fully \emph{symbolic heap} during lazy symbolic execution, 
can improve the scalability of the analysis while maintaining
precision and efficiency. Moreover, the number of path conditions
computed by lazy symbolic execution when a symbolic heap
is used
produces considerably fewer path conditions -- a valuable benefit
for client analyses that use the results of symbolic execution,
e.g., regression analyses.
\end{comment}

In this work, we present a novel heap initialization and analysis
technique which takes inspiration from both approaches and constructs
precise heap summaries lazily during symbolic execution. \nsr{needs
  some text on the fact we use java lite to formalize the heap
  summary, some key characteristicss of the heap such as the fact it
  is a bipartiate graph with locations and referneces, properties of
  the heap such as the determinism and immutability}

Our symbolic heap representation is expressive and can represent
recursive data structures.  \nsr{Is any part of the formalism borrowed
  from the dilligs? Which part are unique?}  \nsr{end on a couple
  sentences about the various rules that will be talked about in the
  paper}\nsr{The reader should be convinced about our expressiveness
  claim here}

We prove that our technique is precise, at any given point during
symbolic execution, the symbolic heap represents the exact set of
feasible concrete heap structures for the program under analysis, and
\nsr{a paragraph that provides intution on how we are a bisumulation
  with the GSE..reader should be convinced about the precision claim}

Our demonstrate the scalability of our approach. Our technique reduces
the points of non-determinism compared to generalized symbolic
execution and explores each control-flow path only once for any given
set of isomorphic heaps \nsr{a paragraph that provides a breif summary
  of the results.. would be nice if we have numbers for lazier and
  lazier Sharp as well.}

\begin{comment}

The key advantages of our approach to lazy symbolic execution
using a fully symbolic heap include:
\begin{itemize}
\item{\emph{Scalability.} Our approach constructs the symbolic
heap on-the-fly during symbolic execution and avoids creating
the additional points of non-determinism
introduced by existing lazy initialization techniques. Moreover, it explores
each execution path only once for any given set of isomorphic heaps.}
\item{\emph{Precision.} At any given point during symbolic execution, 
the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis}
\item{\emph{Expressiveness.} The symbolic heap can represent recursive 
data structures  and heap structures resulting from loops and recursive control 
structures in the analyzed code. }
 \end{itemize}
\end{comment}
